Demystifying the Computer Science \\Ph.D. Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-12 phd-cs-us.tex
updates

\documentclass[11pt]{article}
\usepackage[margin=1.1in]{geometry}
%\usepackage[small,compact]{titlesec} %very powerful
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{cite}
%\usepackage{caption}
%\captionsetup{font=small}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue,
}
\usepackage{booktabs}

@@

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023).  $^*$ indicates the university has a \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese prof.} that can advise CS Ph.D. students.}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign$^*$  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University$^*$ \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor   & 32& George Mason University$^*$\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University$^*$ &37&  Ohio State University\\
    13 & University of Wisconsin - Madison$^*$  &38& Texas A\&M University$^*$ \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania$^*$ &42 & University at Buffalo\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst$^*$ & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech$^*$  \\
    22 & University of Southern California &47&  Arizona State University$^*$ \\
    23 & Stony Brook University$^*$ &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina$^*$ \\
    \bottomrule
    \end{tabular}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage[margin=1.1in]{geometry}
%\usepackage[small,compact]{titlesec} %very powerful
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{caption}
\captionsetup{font=small}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=blue,
}
\usepackage{booktabs}

@@

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023). \red{$^*$} indicates the university has a \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese prof.} that can advise CS Ph.D. students.}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign\red{$^*$}  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University\red{$^*$} \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor\red{$^*$}   & 32& George Mason University\red{$^*$}\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University\red{$^*$} &37&  Ohio State University\\
    13 & University of Wisconsin - Madison\red{$^*$}  &38& Texas A\&M University\red{$^*$} \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania\red{$^*$} &42 & University at Buffalo\red{$^*$}\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst\red{$^*$} & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech\red{$^*$}  \\
    22 & University of Southern California &47&  Arizona State University\red{$^*$} \\
    23 & Stony Brook University\red{$^*$} &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina\red{$^*$} \\
    \bottomrule
    \end{tabular}
\end{table}
